---
title: "Personal ggplot themes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

The themes work using the ggplot2 theme function.

```{r load_library}
library(ggplot2)
```

They are loaded as additional functions to the environment.

```{r import themes}
source("theme_mkw.R")
```

## Simple theme

Theme is named `theme_mkw()` after the creator. All elements are black or white except for grid lines. The legend is placed at the top of the plot by default.

```{r mkw_theme}
iris |> 
  ggplot(aes(x = Sepal.Length, y = Sepal.Width, col = Species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  theme_mkw()
```

### With grid lines

Grid lines can be enabled using the `grid = TRUE` parameter.

```{r mkw_grid}
iris |> 
  ggplot(aes(x = Sepal.Length, y = Sepal.Width, col = Species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  theme_mkw(grid = TRUE)
```

### Facetted plots

The title boxes at the top of facets have a grey fill to make it clear which plot they refer to.

```{r facet_demo}
iris |> 
  ggplot(aes(x = Sepal.Length, y = Sepal.Width, col = Species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(~Species) +
  theme_mkw()
```

```{r}
mtcars |> 
  ggplot(aes(x = hp, y = mpg, col = factor(gear))) +
  geom_point() +
  facet_grid(am ~ cyl) +
  labs(title = "Fuel Economy against Power",
       subtitle = "Facetted by number of cylinders and whether the vehicle is automatic",
       x = "Power (hp)", y = "Fuel Econonmy (mpg)", col = "Number of Gears") +
  theme_mkw()
```

